Total Score

### 2022-11-30 src/MSAtotal_scores.Rmd
read in real estate and landlord score data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r}
# create table with category scores
# isolating score from each category data sheet
real_estate_score <- real_estate_score_data %>% 
  select(cbsa, real_estate_score)

category_score <- landlord_score_data %>% 
  select(MSA, cbsa, landlord_score) %>% 
  inner_join(real_estate_score)

```{r}
category_weights <- c(0.4, 0.25, 0.15, 0.10, 0.10)
```

```{r}
size <- dim(category_score)

for (i in 1:size[1]) {
  MSA_x_data <- c(category_score$real_estate_score[i],
                  category_score$financial_score[i],
                  category_score$landlord_score[i],
                  category_score$climate_impact_score[i], 
                  category_score$energy_score[i]
                  )
  category_score$total_score[i] = weighted.mean(MSA_x_data, category_weights)
}
